Chlorophylla

### 2019-08-02 Chlorophyll.Rmd
chloro

# # With the chloro pixels filter, it is now faster to create the daily data
# daily_chloro_data <- daily_chloro_match %>%
#   dplyr::mutate(date = as.Date(date)) %>%
#   dplyr::group_by(combi, lon, lat, date) %>%
#   dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>%
#   dplyr::group_by(combi, lon, lat) %>%
#   tidyr::nest() %>%
#   dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
#                      climatologyPeriod = c("2002-07-13", "2018-12-04"), # This doesn't mean anything, but the function needs it to work
#                      maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
#   dplyr::select(-data) %>%
#   tidyr::unnest() %>%
#   select(-doy, -seas, -thresh)

>>>>

# # With the chloro pixels filter, it is now faster to create the daily data
daily_chloro_data <-  %>%
  dplyr::mutate(date = as.Date(date)) %>%
  dplyr::group_by(combi, lon, lat, date) %>%
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>%
  dplyr::group_by(combi, lon, lat) %>%
  tidyr::nest() %>%
  dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
                     climatologyPeriod = c("2002-07-13", "2018-12-04"), 
                     maxPadLength = 8)) %>% 
  dplyr::select(-data) %>%
  tidyr::unnest() %>%
  select(-doy, -seas, -thresh)
